%-------------------------
% Resume in Latex
% Author : Pradeep Dantuluri
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\rightmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\pubItem}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} &   \\
      \textit{\small#2} &   \\
      \small#3 &  \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://iswetha522.github.io}{\Large Saraswathi Devi Kalidindi}}  & \textbf{Mobile} : +91 9949912099 \\
   \vspace{14pt}
  \textbf{Email} : \href{mailto:saruk589@gmail.com}{saruk589@gmail.com}\\
  
  
\end{tabular*}

\vspace{10pt}

%-------- SKILLS------------

\vspace{-10pt}
\section{}
 \resumeSubHeadingListStart
    \item{
     \textbf{Expertise}{: Windows OS, Linux OS, MySQL, Eclipse, Manual Testing, Selenium, TFS, Core Java}
    }
    
 \resumeSubHeadingListEnd
 
 \section{Professional Summary}
    {Around 3 years of experience in the field of software testing. Prepared \textbf{Test Scenarios, Test Cases \& Test Data for Functional and Regression Testing}. I am looking forward to join an esteemed organization which allows me to improve my knowledge and experience while contributing to the team after a parenting break.}
    \resumeItemListStart
        \item{Experience in testing \textbf{Client Server and Web based applications} using \textbf{manual testing and
automation testing}.}
        \item{Experience in understanding and analyzing test requirements.}
        \item{Experience in analyzing changes and identifying areas of the application to be \textbf{regression
tested}.}
        \item{Knowledge on different levels of testing like Smoke Testing, Regression Testing, User Acceptance
Testing}
        \item{Good understanding of \textbf{Test Planning, Test Design, Test Execution and Defect Reporting \&​ Tracking}.}
        \item{Knowledge in automating \textbf{Web Applications using Selenium WebDriver}.}
        \item{Basic knowledge of \textbf{SQL} and hands on experience on backend testing.}
        \item{Experience in \textbf{generating reports and graphs}.}
        \item{Good knowledge on software development life cycle[\textbf{SDLC}], software testing lifecycle[\textbf{STLC}] and bug/defect life cycle.}
        \item{Involved in developing \textbf{Automation framework}.}
        \item{Experience in creating UAT test case \& test scripts.}
        \item{Effective communication skills, quick learner, self-motivated and team player.}
        
    \resumeItemListEnd
    
 

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MeridianSoft Info Systems}{Hyderabad, India}
      {Software Test Engineer} {03/2011 - 11/2013}
      
      \textbf{Project - Tradier}
      \resumeItemListStart
        \item{Requirement analysis and test case preparation.}
        \item{Review of test scenarios and test cases.}
        \item{Automated and updated test cases based on implementation changes.}
        \item{Creation of test data using automation scripts for the functional testing team.}
        \item{Involved in executing the test scripts on the new build by using Selenium Webdriver with TestNG.}
        \item{Involved in modification of the framework.}
     \resumeItemListEnd
     \pagebreak
     \textbf{Project - Tradeking}
      \resumeItemListStart
        \item{Performed functional testing on functionality of the application and created test scenarios, test cases, test data for the application.}
        \item{Coordination with the team to ensure the completion of testing phases which include System,
            Integration, Performance, Stress, Usability and Regression testing.}
        \item{Track testing issues and ensure that the product meets the quality standards set by the customer,operations and support groups.}
        \item{Track and address bugs identified in testing and production. Evaluate effectiveness of bug
            resolutions to assign closure status or need for rework.}
        \item{Created the test summary report after the completion of the testing cycle.}
        \item{Experience in creating UAT test cases and detailed test cases.}
        \item{Experience in tracking the whole E2E testing life cycle.}
        \item{Data validation performed for the provided test data requests.}
        \item{Used TFS tool for bug tracking and reporting.}
     \resumeItemListEnd
    
    \resumeSubheading
      {The Pregnancy Pause}{Hyderabad, India}
      {Maternity Leave}{12/2013 - Present}
      \resumeItemListStart
        \item{Maternity break taking care of my kid.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {St.Theressa Institute of Engineering \& Technology }{Visakhapatnam, India}
      {Bachelor of Technology, Computer Science}{ 09/2005 - 04/2009}     
      \resumeItemListStart
        \item{Relevant Courses: C Programming and Data Structures, Advanced Data Structures, Unix and Shell Programming, Object Oriented Programming (Java), Probability and Statistics, Data Warehousing and Data Mining, Database Management Systems}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------------
\section{Achievements}
  \resumeSubHeadingListStart
        \item{Awarded Best Employee for the 3rd Quarter of 2013, MeridianSoft Info Systems, Hyderabad, India}
  \resumeSubHeadingListEnd
  



%-----------Languages-----------------
\section{Languages}
 \resumeSubHeadingListStart
    \item{
     \textbf{English}{: Professional Working Proficiency}
    }

    \item{
     \textbf{Hindi}{: Professional Working Proficiency }
    }

    \item{
     \textbf{Telugu}{: Native or Bilingual Proficiency }
    }
 \resumeSubHeadingListEnd
 

%-----------Interests-----------------
\section{Interests}
 \resumeSubHeadingListStart
    \item{
     {Cooking, Singing, Listening to Music}
    }
 \resumeSubHeadingListEnd
  
%-------------------------------------------
\end{document}
