%-------------------------
% Resume in Latex
% Author : Pradeep Dantuluri
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\rightmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\pubItem}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} &   \\
      \textit{\small#2} &   \\
      \small#3 &  \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://iswetha522.github.io}{\Large Vijayalakshmi Kalidindi}}  & \textbf{Mobile} : +31 6388 62904 \\
   \vspace{14pt}
  \textbf{Email} : \href{mailto:iswetha522@gmail.com}{iswetha522@gmail.com} & \textbf{Github} : {\href{https://github.com/iswetha522}{github.com/iswetha522}} \\
  \textbf{Linkedin} : {\href{https://www.linkedin.com/in/vijayalakshmi-kalidindi/}{linkedin.com/in/vijayalakshmi-kalidindi}} & \textbf{Medium} : {\href{https://iswetha522.medium.com/}{iswetha522.medium.com}}\\
  
\end{tabular*}

\vspace{14pt}

%-------- SKILLS------------

\vspace{-14pt}
\section{}
 \resumeSubHeadingListStart
    \item{
     \textbf{Expertise}{: Data Analysis, Google Tag Manager, Google Analytics, Google Data Studio, JavaScript, Python, Pandas, Numpy, TensorFlow,
     Scikit-Learn, MySQL, Tableau, Microsoft Azure Application Insights, Git}
    }
    
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RelevantOnline BV}{Utrecht, Netherlands}
      {Technical Web Analyst}{10/2021 - Present}
      \resumeItemListStart
        \item{Responsibilities include setting up web analytics and data layer, designing and building datasets integrating new data management tools, analysing data and generating dashboards and reports.}
        \item{Used Google Analytics and Google Data Studio tools to track, report, and analyse website performance, customer trends, and visitor behaviour. }
        \item{Used Google Tag Manager to setup web containers.}
        \item{Experience working with both Google Universal Analytics and Google Analytics 4 to capture user interactions.}
    
      \resumeItemListEnd
  
    \resumeSubheading
      {510 - An initiative of the Netherlands Red Cross}{Den Haag, Netherlands}
      {Data Analyst Volunteer}{06/2021 - 10/2021}
      \resumeItemListStart
        \item{Responsibilities include creating and maintaining web analytics dashboards using Azure Application Insights for the 121 platform, a disaster management app from 510.}
      \resumeItemListEnd

    \resumeSubheading
      {Ironhack}{Amsterdam, Netherlands}
      {Data Analytics Boot-camper}{10/2020 - 12/2020}
      \resumeItemListStart
        \item{Data cleaning and wrangling, statistical analysis, business intelligence, storytelling, machine learning with Python, MySQL and other tools.}
        \item{My final project was Landmark Recognition where I used machine learning techniques to detect a landmark from a given image.}
        \item{Models were trained using Convolutional Neural Network(CNN) and seeded with transfer learning from ResNet50 pre-trained models.}
        \item{\textbf{\href{https://github.com/iswetha522/Landmark_Recognition_Project}{Source code} - \href{https://iswetha522.medium.com/landmark-recognition-final-project-at-ironhack-amsterdam-cad0ad1c27e0}{Medium post}}}
      
      \resumeItemListEnd
    
    \resumeSubheading
      {The Pregnancy Pause}{Hyderabad, India}
      {Maternity Leave}{03/2017 - 10/2020}
      \resumeItemListStart
        \item{Maternity break taking care of my kid.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Yantranet Technologies}{Visakhapatnam, India }
      {Software Engineer}{01/2015 - 02/2017}
      
    Yantranet provides cloud-based IoT solutions such as Digital Signage, Kiosk \& Cloud Analytics that sit on top of a custom-built IoT platform.
      \resumeItemListStart
        \item{Created a Python based API (RESTful Web Service) using Django and MySQL to track device registrations and perform analysis, improving visibility of growth within the company.}
        \item{Designed e-mail marketing campaigns using HTML and CSS, increasing the CTR for outbound campaigns by 30\%.}
        \item{Prepared and supervised customers relationship management databases (MySQL).}
      
      \resumeItemListEnd
    \pagebreak
    \resumeSubheading
      {HCL career development centre}{Chennai, India}
      {Junior Software Developer - Trainee}{04/2013 - 09/2013}
      \resumeItemListStart
        \item{My time at HCL involved preparing web pages and attending training for tools and technologies in Web Develop.}
        \item{Created and Maintained static web pages and templates using JSP, HTML and CSS.}
        \item{Completed training for JSP, HTML \& CSS.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ironhack Amsterdam}{Amsterdam, Netherlands}
      {Data Analytics Boot-camp}{ 10/2020 - 12/2020}  
      \resumeItemListStart
        \item{Data Analysis using Python (NumPy, Pandas) \& MySQL, Data Wrangling, Data Cleaning, API's \& Web Scraping, Inferential Statistics in Python \& Business Intelligence, Data Visualization (Tableau, Matplotlib, Seaborn \& Plotly), Build, Evaluate \& Deploy Machine Learning Models and Pipelines (Scikit-Learn \& TensorFlow)}
       
      
      \resumeItemListEnd
      
    \resumeSubheading
      {Jawaharlal Nehru Technological University, Kakinada }{Visakhapatnam, India}
      {Bachelor of Technology, Computer Science}{ 08/2009 - 05/2013}     
      \resumeItemListStart
        \item{Relevant Courses: C Programming and Data Structures, Advanced Data Structures, Unix and Shell Programming, Object Oriented Programming (Java), Probability and Statistics, Data Warehousing and Data Mining, Database Management Systems}
       
      
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------------
\section{Extra-curricular Activities}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Indian Institute of Management, Visakhapatnam}{Visakhapatnam, India}
      {Women Start-up Programme 2018}{04/2018 - 04/2018}
      \resumeItemListStart
        \item{Selected among the Top 100 for First Boot-camp at Indian Institute of Management, Visakhapatnam initiated by N S Raghavan Centre for Entrepreneurial Learning(NSRCEL) with a participation of 6000+ contestants.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Chegg}{Hyderabad, India}
      {Subject Matter Expert}{02/2016 - 05/2016}
      \resumeItemListStart
        \item{Coached 100+ high school students on Advanced Mathematics and Programming and conducted sessions to clear questions from assignments.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
  



%-----------Languages-----------------
\section{Languages}
 \resumeSubHeadingListStart
    \item{
     \textbf{English}{: Professional Working Proficiency}
    }

    \item{
     \textbf{Hindi}{: Professional Working Proficiency }
    }

    \item{
     \textbf{Telugu}{: Native or Bilingual Proficiency }
    }
 \resumeSubHeadingListEnd
 

%-----------Interests-----------------
\section{Interests}
 \resumeSubHeadingListStart
    \item{
     {Reading, Cooking, Travelling, Listening to Music, Running, Hiking}
    }
 \resumeSubHeadingListEnd
  
%-------------------------------------------
\end{document}
